Preschoolers form conventional pacts with each other to communicate about novel shapes

### 2025-01-27 write-ups/kid_tangrams_cogsci_2025/kid_tangrams_cogsci_2025.Rmd
add osf link

Statistical analyses were run in brms [@burkner2018] with weakly informative priors. We present the estimate and 95% credible intervals. The experimental set-up, analysis code, de-identified transcripts, and performance data for both experiments is available at VERONICA SHOULD MAKE AN OSF LINK.

>>>>

Statistical analyses were run in brms [@burkner2018] with weakly informative priors. We present the estimate and 95% credible intervals. The experimental set-up, analysis code, de-identified transcripts, and performance data for both experiments is available at \url{https://osf.io/7d3ne/?view_only=d094ccd6438741bfbcaa7fde9fbb56b2}.
